Figures for Paper

### 2021-09-28 paper_figures.Rmd
HERM

```{css, echo = FALSE}
h1, #TOC>ul>li {
  color: #000000;
    font-weight: bold;
}

@@

cell_types %>% 
  left_join(clean_data_table[,.(sample,
                               UNC13A_3prime_leaf,
                               UNC13A_5prime_1_leaf,
                               disease_group2,
                               disease_tissue)], by = 'sample') %>%
  filter(tissue_clean %in% c("Frontal_Cortex", 
                             "Lumbar_Spinal_Cord", 
                             "Cervical_Spinal_Cord", 
                             "Motor_Cortex", 
                             "Temporal_Cortex")) %>% 
  mutate(inclusion_reads = UNC13A_3prime_leaf + UNC13A_5prime_1_leaf) %>% 
  mutate(unc13a_detected = ifelse(inclusion_reads > 0, yes = "+", no = "-")) %>% 
  filter(disease_group2 %in% c("ALS-TDP","FTLD-TDP")) %>% 
  group_by(disease_group2,tissue_clean) %>% 
  add_count() %>% 
  mutate(n = n / 5) %>% 
  mutate(plot_name = glue::glue("{tissue_clean} \n {n}")) %>% 
  filter(!is.na(inclusion_reads)) %>% 
  unique() %>% 
  ggplot(aes(x = cell, y = deconv, fill = unc13a_detected)) + 
  # geom_point(size = 2,show.legend = F,pch = 21, position = position_jitterdodge(dodge.width=1,jitter.width = 0.3))+
  geom_boxplot(outlier.color = NA) + 
  facet_wrap(~disease_group2+plot_name,scales = 'free') +
  ggpubr::stat_compare_means(label = "p.format",vjust = 1.3) +
  ggpubr::theme_pubr() +
  scale_fill_manual(values = c("#EBC3B9","#b3251f")) + 
  theme(legend.position = 'none') +
  xlab(element_blank())

@@

>>>>

WAFFLES 
```{css, echo = FALSE}
h1, #TOC>ul>li {
  color: #000000;
    font-weight: bold;
}

@@

cell_types %>% 
  left_join(clean_data_table[,.(sample,
                               UNC13A_3prime_leaf,
                               UNC13A_5prime_1_leaf,
                               disease_group2,
                               disease_tissue)], by = 'sample') %>%
  filter(tissue_clean %in% c("Frontal_Cortex", 
                             "Lumbar_Spinal_Cord", 
                             "Cervical_Spinal_Cord", 
                             "Motor_Cortex", 
                             "Temporal_Cortex")) %>% 
  mutate(inclusion_reads = UNC13A_3prime_leaf + UNC13A_5prime_1_leaf) %>% 
  mutate(unc13a_detected = ifelse(inclusion_reads > 0, yes = "+", no = "-")) %>% 
  filter(disease_group2 %in% c("ALS-TDP","FTLD-TDP")) %>% 
  group_by(disease_group2,tissue_clean) %>% 
  add_count() %>% 
  mutate(n = n / 5) %>% 
  mutate(plot_name = glue::glue("{tissue_clean} \n {n}")) %>% 
  filter(!is.na(inclusion_reads)) %>% 
  unique() %>% 
  ggplot(aes(x = cell, y = deconv, fill = unc13a_detected)) + 
  # geom_point(size = 2,show.legend = F,pch = 21, position = position_jitterdodge(dodge.width=1,jitter.width = 0.3))+
  geom_boxplot(outlier.color = NA) + 
  facet_wrap(~disease_group2+plot_name,scales = 'free') +
  ggpubr::stat_compare_means(label = "p.signif",vjust = 1.3,
hide.ns=TRUE) +
  ggpubr::theme_pubr() +
  scale_fill_manual(values = c("#EBC3B9","#b3251f")) + 
  theme(legend.position = 'none') +
  xlab(element_blank())

@@

# Endogenous SHSY5Y iCLIP

```{r}
# Read in filtered bed file (iMAPs output, filtered by script in pre-processing scripts folder)
sh <- read_csv(paste0(here(), "/data/iCLIP/shsy5y_tdp43_iclip_unc13a_b_only.csv"))

unc13a <- sh %>%
  filter(chr == "chr19" & start > 17599327 & ((end.x < 17690344 & end.y == 0) | 
                                                (end.y < 17690344 & end.x == 0))) %>%
  select(start,total) %>%
  full_join(data.frame(start=17599327:17690344)) %>%
  arrange(start)

unc13a[is.na(unc13a)] <- 0

window <- 20
p_a <- ggplot(unc13a, aes(x = start, y = zoo::rollmean(total, k = window, na.pad=T))) +
  geom_line(alpha = 1) +
  ylim(0, NA) +
    # red dashed line shows position of CE
  geom_vline(xintercept = 17642430, linetype="dashed", alpha= 0.8, size=2, colour="red") +
    # blue line shows position of retained intron
  geom_vline(xintercept = 17628569, linetype="dashed", alpha= 0.8, size=2, colour="blue") +
  ggtitle("UNC13A") +
  ylab(paste("Average XL density in", window, "nt window")) +
  theme_minimal() +
  theme(panel.grid.minor = element_line(size = 0.5), 
        panel.grid.major.x = element_line(size = 0.7,color = 'grey')) +
    theme(axis.text = element_text(size = 28,color = "black"))

unc13b <- sh %>%
  filter(chr == "chr9" & start > 35160008 & ((end.x < 35407338 & end.y == 0) | 
                                                (end.y < 35407338 & end.x == 0))) %>%
  select(start,total) %>%
  full_join(data.frame(start=35160008:35407338)) %>%
  arrange(start)

unc13b[is.na(unc13b)] <- 0

p_b = ggplot(unc13b, aes(x = start, y = zoo::rollmean(total, k = window, na.pad=T))) +
  geom_line(alpha = 1) +
  ylim(0, NA) +
    # red dashed line shows rough position of UG-repeat near fsE
  geom_vline(xintercept = 35364641, linetype="dashed", alpha= 0.8, size=2, colour="red") + 
      # blue dashed line shows start of intron

  geom_vline(xintercept = 35384315, linetype="dashed", alpha= 0.8, size=2, colour="blue") +

  theme_minimal() + 
  theme(panel.grid.minor = element_line(size = 0.5), 
        panel.grid.major.x = element_line(size = 0.7,color = 'grey')) +
  ggtitle("UNC13B") +
  ylab(paste("Average XL density in", window, "nt window")) +
  theme(axis.text = element_text(size = 28,color = "black"))

p_a + p_b
